Quantizing the Bosonic String on a Loop Quantum Gravity Background

### 2024-01-03 lqg-strings.tex
Typo

As usual, by the appearance of the Minkowski metric in the non-zero commutator
\begin{equation} \label{eqn:ghosts}
	\Big[ \Hat{a}^{\mu} _{p} , (\Hat{a}^{\nu} _{k})^{\dagger} \Big] = \eta ^{\mu \nu} \delta _{p k} ,
\end{equation}
we have ghosts in the theory which must be dealt with. When translating the constraints as quantum operators, we require that they have vanishing matrix elements when sandwiched by physical states $\psi$ and $\phi$:
\begin{equation} \label{eqn:L-constraint-quantum-1}
	\bra{\phi} \Hat{L}_{p , k} \ket{\psi} = 0 \, \,
\end{equation}
\begin{equation} \label{eqn:L-constraint-quantum-2}
	\bra{\phi} \Hat{\widetilde{L}}_{p , k} \ket{\psi} = 0 .
\end{equation}
$\Hat{L}_{p , k}$ has no ambiguities since it's composed of only annihilation operators, however, we have an ambiguity for $\Hat{\widetilde{L}}_{p , 0}$. To resolve this issue, we pick
\begin{equation} \label{eqn:L-normal-ordering}
	\Hat{\widetilde{L}}_{p , 0} = \frac{- p}{E_{- p}} (\Hat{\alpha}^{\mu} _{p})^{\dagger} \Hat{\alpha}^{\nu} _{p} \eta _{\mu \nu}
\end{equation}
with the annihilation operator to the right, which manifests in the imposition of the constraint as
\begin{equation} \label{eqn:shifted-L-constraint}
	\bra{\phi} \Hat{\widetilde{L}}_{p , 0} - c_{p} \ket{\psi} = 0 ,
\end{equation}
for some sequence $c_{p}$. The reason for it to be a sequence of $p$ and not a constant like in the regular String Theory literature is that in the usual theory, we would have a sum over $p$ and thus it would end up being a constant, but in our analysis we have this extra freedom, which we'll now see ends up being important. Classically, we had eq(\ref{eqn:string-rest-mass}) for the string rest mass, which we can rewrite as
\begin{equation} \label{eqn:alternative-classical-rest-mass}
	M^2 = - \frac{1}{(4 \pi (\alpha ')^2)^2} \lim _{n \rightarrow 0} \left( - \frac{E_{p}}{p} \widetilde{L}_{p , 0} \right) ,
\end{equation}
from where we can now see that the string mass spectrum will get shifted by
\begin{equation} \label{eqn:shifted-mass-spectrum}
	\Hat{M}^2 = - \frac{1}{(4 \pi (\alpha ')^2)^2} \left( (\Hat{\alpha} ^{\mu} _{0})^{\dagger} \Hat{\alpha}^{\nu} _{0} \eta _{\mu \nu} + \lim _{p \rightarrow 0} \frac{E_{p}}{p} c_{p} \right) .
\end{equation}
Since $E_{0} = \mu$, it seems like the natural candidate for $c_{p}$ would be some function $f (\mu , p)$ such that
\begin{equation} \label{eqn:cp-limit}
	\lim _{p \rightarrow 0} \frac{c_{p}}{p} = \mu
\end{equation}
like $c_{p} = \mu p$, $c_{p} = \sin (\mu p)$, $c_{p} = \tan (\mu p)$, etc, making it so the mass spectrum of the string gets shifted by the \textquotedblleft mass" term of the Klein-Gordon equation (\ref{eqn:X-Klein-Gordon-eqn}), $\mu ^2$.

>>>>

As usual, by the appearance of the Minkowski metric in the non-zero commutator
\begin{equation} \label{eqn:ghosts}
	\Big[ \Hat{a}^{\mu} _{p} , (\Hat{a}^{\nu} _{k})^{\dagger} \Big] = \eta ^{\mu \nu} \delta _{p k} ,
\end{equation}
we have ghosts in the theory which must be dealt with. When translating the constraints as quantum operators, we require that they have vanishing matrix elements when sandwiched by physical states $\psi$ and $\phi$:
\begin{equation} \label{eqn:L-constraint-quantum-1}
	\bra{\phi} \Hat{L}_{p , k} \ket{\psi} = 0 \, \,
\end{equation}
\begin{equation} \label{eqn:L-constraint-quantum-2}
	\bra{\phi} \Hat{\widetilde{L}}_{p , k} \ket{\psi} = 0 .
\end{equation}
$\Hat{L}_{p , k}$ has no ambiguities since it's composed of only annihilation operators, however, we have an ambiguity for $\Hat{\widetilde{L}}_{p , 0}$. To resolve this issue, we pick
\begin{equation} \label{eqn:L-normal-ordering}
	\Hat{\widetilde{L}}_{p , 0} = \frac{- p}{E_{- p}} (\Hat{\alpha}^{\mu} _{p})^{\dagger} \Hat{\alpha}^{\nu} _{p} \eta _{\mu \nu}
\end{equation}
with the annihilation operator to the right, which manifests in the imposition of the constraint as
\begin{equation} \label{eqn:shifted-L-constraint}
	\bra{\phi} \Hat{\widetilde{L}}_{p , 0} - c_{p} \ket{\psi} = 0 ,
\end{equation}
for some sequence $c_{p}$. The reason for it to be a sequence of $p$ and not a constant like in the regular String Theory literature is that in the usual theory, we would have a sum over $p$ and thus it would end up being a constant, but in our analysis we have this extra freedom, which we'll now see ends up being important. Classically, we had eq(\ref{eqn:string-rest-mass}) for the string rest mass, which we can rewrite as
\begin{equation} \label{eqn:alternative-classical-rest-mass}
	M^2 = - \frac{1}{(4 \pi (\alpha ')^2)^2} \lim _{p \rightarrow 0} \left( - \frac{E_{p}}{p} \widetilde{L}_{p , 0} \right) ,
\end{equation}
from where we can now see that the string mass spectrum will get shifted by
\begin{equation} \label{eqn:shifted-mass-spectrum}
	\Hat{M}^2 = - \frac{1}{(4 \pi (\alpha ')^2)^2} \left( (\Hat{\alpha} ^{\mu} _{0})^{\dagger} \Hat{\alpha}^{\nu} _{0} \eta _{\mu \nu} + \lim _{p \rightarrow 0} \frac{E_{p}}{p} c_{p} \right) .
\end{equation}
Since $E_{0} = \mu$, it seems like the natural candidate for $c_{p}$ would be some function $f (\mu , p)$ such that
\begin{equation} \label{eqn:cp-limit}
	\lim _{p \rightarrow 0} \frac{c_{p}}{p} = \mu
\end{equation}
like $c_{p} = \mu p$, $c_{p} = \sin (\mu p)$, $c_{p} = \tan (\mu p)$, etc, making it so the mass spectrum of the string gets shifted by the \textquotedblleft mass" term of the Klein-Gordon equation (\ref{eqn:X-Klein-Gordon-eqn}), $\mu ^2$.
